Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-09-15 SubGenome Analysis.Rmd
Comparing based on expression

```{r diffExpression_subgenome, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
# Expression Diffs
grid.newpage()
g <- draw.pairwise.venn(
  area1 = expressedPairs %>% subset((FPKM_mean1/FPKM_mean2) < 2) %>% nrow(),
  area2 = expressedPairs %>% subset((FPKM_mean2/FPKM_mean1) < 2) %>% nrow(),
  cross.area = intersect(expressedPairs %>% subset((FPKM_mean1/FPKM_mean2) < 2),
                         expressedPairs %>% subset((FPKM_mean2/FPKM_mean1) < 2)) %>%
                          nrow(), 
  category = c("Sub1", "Sub2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="Genes with 2-fold higher\nexpression by subgenome")
```

>>>>

```{r diffExpression_subgenome, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4, fig.align='center'}
# Expression Diffs
grid.newpage()
g <- draw.pairwise.venn(
  area1 = expressedPairs %>% subset((FPKM_mean1/FPKM_mean2) < 2) %>% nrow(),
  area2 = expressedPairs %>% subset((FPKM_mean2/FPKM_mean1) < 2) %>% nrow(),
  cross.area = intersect(expressedPairs %>% subset((FPKM_mean1/FPKM_mean2) < 2),
                         expressedPairs %>% subset((FPKM_mean2/FPKM_mean1) < 2)) %>%
                          nrow(), 
  category = c("Sub1", "Sub2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="Genes with 2-fold higher\nexpression by subgenome")
```

Overall expression patterns between subgenome 1 and subgenome 2 are highly similar.  Below we show to views of the same data.  In the density graph, we can see that subgenome 1 is slightly shifted to the right of subgenome 2 expression, but otherwise follows the same shape.  Viewed as a boxplot, you can again see that the quartiles in subgenome 1 and 2 are largely the same.  This also shows a few high expressing outliers on subgenome 1.

```{r subgenome_expression_frequency, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4.5, fig.height=4}
## Plot frequency of isoform counts for each gene
data <- expressedGenes %>% inner_join(subgenome, by=c("geneID"="gene2")) %>% select(geneID, FPKM_mean, subgenome) %>% filter(subgenome=="sub1" | subgenome=="sub2")
ggplot(data, aes(FPKM_mean,color=subgenome)) + 
  geom_density() + 
  scale_x_log10() +
  labs(y = "Density (FPKM)", 
       x = "log10(FPKM)", 
       title = "Comparison of FPKM Expression between\nGenes in Subgenome 1 and Subgenome 2"
  )

ggplot(data, aes(subgenome,log10(FPKM_mean))) +
  geom_boxplot() +
  labs(y = "log10(FPKM)",
       x = "Subgenome",
       title = "Comparison of FPKM Expression between\nGenes in Subgenome 1 and Subgenome 2"
  )
```
